Learning Discrete Bayesian Networks from Continuous Data

### 2016-08-09 rebuttal/rebuttal.tex

On the other hand, if the relation between $X$ and $Z$ is understood as $X \leftarrow Z$, then $X_1$ and $X_2$ are not d-separated:

$$X_1 \leftarrow Z_1 \rightarrow Z_2 \rightarrow X_2$$

However, if this is the case, the framework discussed in this paper appears to be closely related to [2]. More specifically, [2] also considers learning the BN structure and learning the discretization of the data simultaneously, consider the same type of discretization policy as this paper. However [2] only sets up the learning problem, but do not provide any algorithm to solve it.\\

[1] Lustgarten, Jonathan L., et al. ``Application of an efficient Bayesian discretization method to biomedical data.'' BMC bioinformatics 12.1 (2011): 1.

[2] Monti, Stefano, and Gregory F. Cooper. ``A multivariate discretization method for learning Bayesian networks from mixed data.'' UAI. 1998.

@@

\noindent\rule{8cm}{0.4pt}\\
{\bf Reviewer \#2} \\

In the experiment session, three datasets with known network structures are used to show that the proposed method learns better than previous work on MDL-based discretization by [3]. More specifically, the paper first assumes given Bayesian network structures, and compares its discretization results with the MDL discretization in [3]. The experiment results show that the proposed approach learns a discretization with a notable higher log-likelihood than the MDL discretization (i.e., the proposed approach learns a discretization such that the known BN structure with the discretized variable has a higher log-likelihood). The paper then learns BNs with both its proposed discretization and an uniform discretization, and compare the learned BNs. Here, in the current form of the manuscript, it does not appear to be clear if the proposed discretization learned a better BN (in terms of say comparing to the ground truth). Moreover, I believe the effectiveness of the proposed method would be more strongly supported if the scale of the experiment is larger, especially given the experimental results on two additional dataset in the appendix, where the performance of the proposed approach is similar to the MDL approach by [3].

In sum, I believe this paper has some promising ideas. However, I would appreciate if the proposed approach is justified better (such as the semantics of the discretization), and its relation to prior work clarified better (particularly with [2]). Further, I would appreciate if the experiments provide a broader evaluation to claim that the paper improves on the state-of-the-art.\\

[3] Friedman, Nir, and Moises Goldszmidt. ``Discretizing continuous attributes while learning Bayesian networks.'' Icml. 1996.

### 2016-08-09 Learning_Discrete_Bayesian_Networks_from_Continuous_Data.tex
incorporating Mykel edits

where larger values of $L$ encourage more discretization intervals.
This prior encourages edges between well-separated values over edges between closely packed samples.
All following content sets $L$ to the largest number of intervals among discrete variables in $\cX$'s Markov blanket, which encourages Bayesian networks with consistent interval counts.
Higher values of $L$ can be used when the continuous variable requires more discretization intervals than its Markov blanket.

>>>>

where larger values of $L$ encourage more discretization intervals.
This prior encourages edges between well-separated values over edges between closely packed samples.
The experiments in this paper set $L$ to the largest number of intervals among discrete variables in $\cX$'s Markov blanket, which encourages Bayesian networks with consistent interval counts.
Higher values of $L$ can be used when the continuous variable requires more discretization intervals than its Markov blanket.
